UMAP reveals cryptic population structure and phenotype heterogeneity in large genomic cohorts

### 2019-06-18 ms/main.tex
add alt colour for HRS

\begin{figure}
\centering
   \includegraphics[width=0.6\linewidth]{images/HRS_1000G_NP1_UMAP_PC10_NC2_NN15_MD05_pca_1kgp_onto_hrs_umap_1kgp_onto_hrs_2018112221116_admix.pdf}
   \caption{UMAP on the first 10 principal components of HRS data. colouring individuals by estimated admixture from three ancestral populations reveals considerable diversity in the Hispanic population. This projection coloured by self-identified race and Hispanic status is presented in figure~\ref{fig:supp_umap_hrs_eth}. Admixture proportions for each individual were estimated in \cite{baharian2016great} by assuming ancestral African, Asian, and European populations using RFMIX \cite{Maples:2013fia}. We have scaled each of the three proportions to values between 0 and 255 (with 100\% corresponding to 255), to colour individual points by their estimated admixture represented by RGB where red, green, and blue respectively correspond to African, European, and Asian/Native American ancestry.}
    \label{fig:umap_hrs_admix}
\end{figure}

>>>>

\begin{figure}
\centering
   \includegraphics[width=0.6\linewidth]{images/HRS_1000G_NP1_UMAP_PC10_NC2_NN15_MD05_pca_1kgp_onto_hrs_umap_1kgp_onto_hrs_2018112221116_admix.pdf}
   \caption{UMAP on the first 10 principal components of HRS data. colouring individuals by estimated admixture from three ancestral populations reveals considerable diversity in the Hispanic population. This projection coloured by self-identified race and Hispanic status is presented in figure~\ref{fig:supp_umap_hrs_eth}. Admixture proportions for each individual were estimated in \cite{baharian2016great} by assuming ancestral African, Asian, and European populations using RFMIX \cite{Maples:2013fia}. We have scaled each of the three proportions to values between 0 and 255 (with 100\% corresponding to 255), to colour individual points by their estimated admixture represented by RGB where red, green, and blue respectively correspond to African, European, and Asian/Native American ancestry. An alternate colouring is provided in figure~\ref{fig:umap_hrs_admix_alt}}
    \label{fig:umap_hrs_admix}
\end{figure}

\begin{figure}
\centering
   \includegraphics[width=0.6\linewidth]{images/HRS_1000G_NP1_UMAP_PC10_NC2_NN15_MD05_pca_1kgp_onto_hrs_umap_1kgp_onto_hrs_2018112221116_admix132.jpeg}
   \caption{An alternate colouring of \ref{fig:umap_hrs_admix}. Here red, green, and blue correspond to African, Asian/Native American, and European ancestry, respectively.}
    \label{fig:umap_hrs_admix_alt}
\end{figure}
